Pre-Main-Sequence M-Dwarfs With Complex Quasiperiodic Variability From Four Years of TESS

### 2023-06-22 paper/ms.tex
update ms

\paragraph{Connection to close-in exoplanets}
The concordance model for planet formation invokes the presence of an accretion
disk.
The disk is truncated (by what?) at the magnetospheric truncation radius,
which happens to often coincidentally be at the Keplerian corotation radius.
In such a scenario, planetesimals and boulders can migrate inward due to
Type X migration (CITE),
until they hit a ``dust trap'' at the inner wall (CITE eg Kama2009,and
related).
Support for this model comes from the rotation periods of classical
and weak-lined T Tauri stars (CITE Rebull2018,2019);
from near-infrared interferometric observations that detect thermal
emission from the disk wall (CITE CITE);
and from the turn-over in the exoplanet orbital period distribution,
which occurs around 5-10 days for FGK stars, and perhaps even
closer-in for M-dwarfs (CITE Petigura2022, and CITE for M-dwarfs).

@@

>>>>

\paragraph{Connection to debris disk evolution}
The concordance model for planet formation invokes the presence of an accretion
disk.
The disk is truncated (by what?) at the magnetospheric truncation radius,
which happens to often coincidentally be at the Keplerian corotation radius.
In such a scenario, planetesimals and boulders can migrate inward due to
Type X migration (CITE),
until they hit a ``dust trap'' at the inner wall (CITE eg Kama2009,and
related).
Support for this model comes from the rotation periods of classical
and weak-lined T Tauri stars (CITE Rebull2018,2019);
from near-infrared interferometric observations that detect thermal
emission from the disk wall (CITE CITE);
and from the turn-over in the exoplanet orbital period distribution,
which occurs around 5-10 days for FGK stars, and perhaps even
closer-in for M-dwarfs (CITE Petigura2022, and CITE for M-dwarfs).

@@

\paragraph{Connection to close-in exoplanets}
Planet occurrence rate studies based on Kepler showed that around
(early) M-dwarfs, there are $\approx$0.1 planets per star with sizes
between 1-4\,$R_\oplus$ and orbital periods within 3 days
\citep{2015ApJ...807...45D}.
TRAPPIST-1b, a rocky planet with an orbital period of 1.5\,days is a
possible example of this type of planet (CITE), though it orbits a
very low-mass star (0.08\,M$_\odot$).

The connection between the CQV phenomenon and these close-in
exoplanets remains to be made.
If the dust cloud model is correct, then assuming that the
compact multiplanet resonant chains migrate to within $\approx$5-10
stellar radii within the first 100\,Myr (e.g. CITE IZIDORO), the
dust clouds and the planets would coexist for a non-negligible time
interval.
Rocky planets this young likely still have molten global magma oceans
(e.g. CITE LICHTENBERG REVIEW), and would undergo significant 
outgassing and atmospheric escape.
A scenario in which close-in rocky planets serve as a possible source
of dust for the clouds is not entirely implausible, though it remains
to be explored.
